---
title: "Distribution of P-values and Type I Error Rate"
author: "Peiran Zhang"
date: "11/24/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

```{r}
library(car)
library(RNOmni)
library(VGAM)
library(GeneralizedHyperbolic)
library(lsr)
library(lmPerm)
library(pwr)
library(coin)
library(Deducer)

INT_function = function(x, n, k) { 
  output = 0
  ranks = rank(x)
  for (i in 1:n) {
    output[i] = probitlink((ranks[i] - k)/(n + 1 - 2*k))
  }
  return(output)
}
```


## Two Sample Test

## Normal Distribution
```{r}
# Use the given matrix to fit the data generated from standard normal distribution. Construct 1000 simulations. Use 0.05 as significance level and test for sample size 50 and 100 respectively. Return the Type I error rate for both original data and transformed data and display the histograms of the distributions of p-values.

normfunc = function(simulation, n, k, siglevel) { 
  # later functions for all other distributions are constructed in the same way as this one
  X1 = c(rep(1, n/2), rep(0, n/2))
  X2 = c(rep(0, n/2), rep(1, n/2))
  A = matrix(c(X1, X2), nrow = n, ncol=2) # construct the matrix A = [0, 0, 0 ...... 1, 1, 1]
  p_original = vector(length = simulation) # store the p values for original data
  error_original = NA # mark the position where type I error occurs in original data
  p_transformed = vector(length = simulation) # store the p values for transformed data
  error_transformed = NA # mark the position where type I error occurs in transformed data
  
  plot(density(rnorm(50, 0, 1)), main = "Density Curve") # plot the density curve for reference
  for(i in 1 : simulation){ # number of simulations
    original = rnorm(n, 0, 1) # generate data from the desired distribution
    fit_original = lm(formula = original ~ A) # perform the two sample t test
    p_original[i] = summary(fit_original)$coefficients[2,4] # collect the p values
    if (p_original[i] < siglevel) {
      error_original[i] = 1 # mark the errors in order to calculate the type I error rate
    }
    transformed = INT_function(original, n, k) # apply the inverse normal transformation
    fit_transformed = lm(formula = transformed ~ A) # perform the two sample t test again using the transformed data
    p_transformed[i] = summary(fit_transformed)$coefficients[2,4] # collect the p values
    if (p_transformed[i] < siglevel) {
       error_transformed[i] = 1 # mark the errors in testing the transformed data
    }
  }
  print(data.frame("TypeI Error Rate Original" = (length(which(error_original == 1)))/simulation, "TypeI Error Rate Transformed" = (length(which(error_transformed == 1)))/simulation)) # form the table with the type I error rates of the two tests using original and transformed data
  hist(p_original, main = "Distribution of p-values for Original Data")
  hist(p_transformed, main = "Distribution of p-values for Transformed Data")
}

normfunc(1000, 50, 0.4, 0.05)
```
```{r}
normfunc(1000, 100, 0.4, 0.05)
```

## Exponential Distribution
```{r}
# Use the given matrix to fit the data generated from exponential distribution with rate = 1. Construct 1000 simulations. Use 0.05 as significance level and test for sample size 50 and 100 respectively. Return the Type I error rate for both original data and transformed data and display the histograms of the distributions of p-values.

expfunc = function(simulation, n, k, siglevel) {
  X1 = c(rep(1, n/2), rep(0, n/2))
  X2 = c(rep(0, n/2), rep(1, n/2))
  A = matrix(c(X1, X2), nrow = n, ncol=2) 
  p_original = vector(length = simulation)
  error_original = NA
  p_transformed = vector(length = simulation)
  error_transformed = NA
  
  plot(density(rexp(n)), main = "Density Curve")
  for(i in 1 : simulation){
    original = rexp(n)
    fit_original = lm(formula = original ~ A) 
    p_original[i] = summary(fit_original)$coefficients[2,4]
    if (p_original[i] < siglevel) {
      error_original[i] = 1 
    }
    transformed = INT_function(original, n, k) 
    fit_transformed = lm(formula = transformed ~ A)
    p_transformed[i] = summary(fit_transformed)$coefficients[2,4]
    if (p_transformed[i] < siglevel) {
       error_transformed[i] = 1
    }
  }
  print(data.frame("TypeI Error Rate Original" = (length(which(error_original == 1)))/simulation, "TypeI Error Rate Transformed" = (length(which(error_transformed == 1)))/simulation))
  hist(p_original, main = "Distribution of p-values for Original Data")
  hist(p_transformed, main = "Distribution of p-values for Transformed Data")
}

expfunc(1000, 50, 0.4, 0.05)
```
```{r}
expfunc(1000, 100, 0.4, 0.05)
```

## Chi-square Distribution
```{r}
# Use the given matrix to fit the data generated from Chi-square distribution with df = 1. Construct 1000 simulations. Use 0.05 as significance level and test for sample size 50 and 100 respectively. Return the Type I error rate for both original data and transformed data and display the histograms of the distributions of p-values.

chisqfunc = function(simulation, n, k, siglevel) {
  X1 = c(rep(1, n/2), rep(0, n/2))
  X2 = c(rep(0, n/2), rep(1, n/2))
  A = matrix(c(X1, X2), nrow = n, ncol=2)
  p_original = vector(length = simulation)
  error_original = NA
  p_transformed = vector(length = simulation)
  error_transformed = NA
  
  plot(density(rchisq(n, df = 1)), main = "Density Curve")
  for(i in 1 : simulation){
    original = rchisq(n, df = 1)
    fit_original = lm(formula = original ~ A) 
    p_original[i] = summary(fit_original)$coefficients[2,4]
    if (p_original[i] < siglevel) {
      error_original[i] = 1 
    }
    transformed = INT_function(original, n, k) 
    fit_transformed = lm(formula = transformed ~ A)
    p_transformed[i] = summary(fit_transformed)$coefficients[2,4]
    if (p_transformed[i] < siglevel) {
       error_transformed[i] = 1
    }
  }
  print(data.frame("TypeI Error Rate Original" = (length(which(error_original == 1)))/simulation, "TypeI Error Rate Transformed" = (length(which(error_transformed == 1)))/simulation))
  hist(p_original, main = "Distribution of p-values for Original Data")
  hist(p_transformed, main = "Distribution of p-values for Transformed Data")
}

chisqfunc(1000, 50, 0.4, 0.05)
```
```{r}
chisqfunc(1000, 100, 0.4, 0.05)
```




## Other Heavy Tailed Distributions

## LaPlace Distribution
### Use the given matrix to fit the data generated from LaPlace distribution with location = 0 and scale = 1. Use 0.05, 0.01, and 0.001 as significance levels and test for sample size 20, 50, and 100 respectively.
```{r}
laplacefunc = function(simulation, n, k, siglevel) {
  X1 = c(rep(1, n/2), rep(0, n/2))
  X2 = c(rep(0, n/2), rep(1, n/2))
  A = matrix(c(X1, X2), nrow = n, ncol=2)
  p_original = vector(length = simulation)
  error_original = NA
  p_transformed = vector(length = simulation)
  error_transformed = NA
  
  plot(density(rlaplace(n, location = 0, scale = 1)), main = "Density Curve")
  for(i in 1 : simulation){
    original = rlaplace(n, location = 0, scale = 1)
    fit_original = lm(formula = original ~ A) 
    p_original[i] = summary(fit_original)$coefficients[2,4]
    if (p_original[i] < siglevel) {
      error_original[i] = 1 
    }
    transformed = INT_function(original, n, k) 
    fit_transformed = lm(formula = transformed ~ A)
    p_transformed[i] = summary(fit_transformed)$coefficients[2,4]
    if (p_transformed[i] < siglevel) {
       error_transformed[i] = 1
    }
  }
  print(data.frame("TypeI Error Rate Original" = (length(which(error_original == 1)))/simulation, "TypeI Error Rate Transformed" = (length(which(error_transformed == 1)))/simulation))
  hist(p_original, main = "Distribution of p-values for Original Data")
  hist(p_transformed, main = "Distribution of p-values for Transformed Data")
}
laplacefunc(1000, 20, 0.4, 0.05)
```
```{r}
laplacefunc(1000, 20, 0.4, 0.01)
```
```{r}
laplacefunc(1000, 20, 0.4, 0.001)
```
```{r}
laplacefunc(1000, 50, 0.4, 0.05)
```
```{r}
laplacefunc(1000, 50, 0.4, 0.01)
```
```{r}
laplacefunc(1000, 50, 0.4, 0.001)
```
```{r}
laplacefunc(1000, 100, 0.4, 0.05)
```
```{r}
laplacefunc(1000, 100, 0.4, 0.01)
```
```{r}
laplacefunc(1000, 100, 0.4, 0.001)
```

## Weibull Distribution
### Use the given matrix to fit the data generated from Weibull distribution with shape = 1 and scale = 1. Use 0.05, 0.01, and 0.001 as significance levels and test for sample size 20, 50, and 100 respectively.
```{r}
weibullfunc = function(simulation, n, k, siglevel) {
  X1 = c(rep(1, n/2), rep(0, n/2))
  X2 = c(rep(0, n/2), rep(1, n/2))
  A = matrix(c(X1, X2), nrow = n, ncol=2)
  p_original = vector(length = simulation)
  error_original = NA
  p_transformed = vector(length = simulation)
  error_transformed = NA
  
  plot(density(rweibull(n, shape = 1, scale = 1)), main = "Density Curve")
  for(i in 1 : simulation){
    original = rweibull(n, shape = 1, scale = 1)
    fit_original = lm(formula = original ~ A) 
    p_original[i] = summary(fit_original)$coefficients[2,4]
    if (p_original[i] < siglevel) {
      error_original[i] = 1 
    }
    transformed = INT_function(original, n, k) 
    fit_transformed = lm(formula = transformed ~ A)
    p_transformed[i] = summary(fit_transformed)$coefficients[2,4]
    if (p_transformed[i] < siglevel) {
       error_transformed[i] = 1
    }
  }
  print(data.frame("TypeI Error Rate Original" = (length(which(error_original == 1)))/simulation, "TypeI Error Rate Transformed" = (length(which(error_transformed == 1)))/simulation))
  hist(p_original, main = "Distribution of p-values for Original Data")
  hist(p_transformed, main = "Distribution of p-values for Transformed Data")
}

weibullfunc(1000, 20, 0.4, 0.05)
```
```{r}
weibullfunc(1000, 20, 0.4, 0.01)
```
```{r}
weibullfunc(1000, 20, 0.4, 0.001)
```
```{r}
weibullfunc(1000, 50, 0.4, 0.05)
```
```{r}
weibullfunc(1000, 50, 0.4, 0.01)
```
```{r}
weibullfunc(1000, 50, 0.4, 0.001)
```
```{r}
weibullfunc(1000, 100, 0.4, 0.05)
```
```{r}
weibullfunc(1000, 100, 0.4, 0.01)
```
```{r}
weibullfunc(1000, 100, 0.4, 0.001)
```

## Rayleigh Distribution
### Use the given matrix to fit the data generated from Rayleigh distribution with scale = 1. Use 0.05, 0.01, and 0.001 as significance levels and test for sample size 20, 50, and 100 respectively.
```{r}
rayleighfunc = function(simulation, n, k, siglevel) {
  X1 = c(rep(1, n/2), rep(0, n/2))
  X2 = c(rep(0, n/2), rep(1, n/2))
  A = matrix(c(X1, X2), nrow = n, ncol=2)
  p_original = vector(length = simulation)
  error_original = NA
  p_transformed = vector(length = simulation)
  error_transformed = NA
  
  plot(density(rrayleigh(n, scale = 1)), main = "Density Curve")
  for(i in 1 : simulation){
    original = rrayleigh(n, scale = 1)
    fit_original = lm(formula = original ~ A) 
    p_original[i] = summary(fit_original)$coefficients[2,4]
    if (p_original[i] < siglevel) {
      error_original[i] = 1 
    }
    transformed = INT_function(original, n, k) 
    fit_transformed = lm(formula = transformed ~ A)
    p_transformed[i] = summary(fit_transformed)$coefficients[2,4]
    if (p_transformed[i] < siglevel) {
       error_transformed[i] = 1
    }
  }
  print(data.frame("TypeI Error Rate Original" = (length(which(error_original == 1)))/simulation, "TypeI Error Rate Transformed" = (length(which(error_transformed == 1)))/simulation))
  hist(p_original, main = "Distribution of p-values for Original Data with")
  hist(p_transformed, main = "Distribution of p-values for Transformed Data")
}
rayleighfunc(1000, 20, 0.4, 0.05)
```
```{r}
rayleighfunc(1000, 20, 0.4, 0.01)
```
```{r}
rayleighfunc(1000, 20, 0.4, 0.001)
```
```{r}
rayleighfunc(1000, 50, 0.4, 0.05)
```
```{r}
rayleighfunc(1000, 50, 0.4, 0.01)
```
```{r}
rayleighfunc(1000, 50, 0.4, 0.001)
```
```{r}
rayleighfunc(1000, 100, 0.4, 0.05)
```
```{r}
rayleighfunc(1000, 100, 0.4, 0.01)
```
```{r}
rayleighfunc(1000, 100, 0.4, 0.001)
```




## More Heavy Tailed Distributions

## Cauchy Distribution
### Use the given matrix to fit the data generated from Cauchy distribution with location = 0 and scale = 1. Use 0.05, 0.01, and 0.001 as significance levels and test for sample size 20, 50, and 100 respectively. Show a break in uniformity in the distribution of p values.
```{r}
cauchyfunc = function(simulation, n, k, siglevel) {
  X1 = c(rep(1, n/2), rep(0, n/2))
  X2 = c(rep(0, n/2), rep(1, n/2))
  A = matrix(c(X1, X2), nrow = n, ncol=2)
  p_original = vector(length = simulation)
  error_original = NA
  p_transformed = vector(length = simulation)
  error_transformed = NA
  
  plot(density(rcauchy(n, location = 0, scale = 1)), main = "Density Curve")
  for(i in 1 : simulation){
    original = rcauchy(n, location = 0, scale = 1)
    fit_original = lm(formula = original ~ A) 
    p_original[i] = summary(fit_original)$coefficients[2,4]
    if (p_original[i] < siglevel) {
      error_original[i] = 1 
    }
    transformed = INT_function(original, n, k) 
    fit_transformed = lm(formula = transformed ~ A)
    p_transformed[i] = summary(fit_transformed)$coefficients[2,4]
    if (p_transformed[i] < siglevel) {
       error_transformed[i] = 1
    }
  }
  print(data.frame("TypeI Error Rate Original" = (length(which(error_original == 1)))/simulation, "TypeI Error Rate Transformed" = (length(which(error_transformed == 1)))/simulation))
  hist(p_original, main = "Distribution of p-values for Original Data")
  hist(p_transformed, main = "Distribution of p-values for Transformed Data")
}
cauchyfunc(1000, 20, 0.4, 0.05)
```
```{r}
cauchyfunc(1000, 20, 0.4, 0.01)
```
```{r}
cauchyfunc(1000, 20, 0.4, 0.001)
```
```{r}
cauchyfunc(1000, 50, 0.4, 0.05)
```
```{r}
cauchyfunc(1000, 50, 0.4, 0.01)
```
```{r}
cauchyfunc(1000, 50, 0.4, 0.001)
```
```{r}
cauchyfunc(1000, 100, 0.4, 0.05)
```
```{r}
cauchyfunc(1000, 100, 0.4, 0.01)
```
```{r}
cauchyfunc(1000, 100, 0.4, 0.001)
```

## Log Normal Distribution - the uniformity in the distribution of p values is gradually broken as sdlog increases
### Set sdlog = 1. Try different sample sizes
```{r}
lognormfunc = function(simulation, n, k, siglevel) {
  X1 = c(rep(1, n/2), rep(0, n/2))
  X2 = c(rep(0, n/2), rep(1, n/2))
  A = matrix(c(X1, X2), nrow = n, ncol=2)
  p_original = vector(length = simulation)
  error_original = NA
  p_transformed = vector(length = simulation)
  error_transformed = NA
  
  plot(density(rlnorm(n, meanlog = 0, sdlog = 1)), main = "Density Curve")
  for(i in 1 : simulation){
    original = rlnorm(n, meanlog = 0, sdlog = 1)
    fit_original = lm(formula = original ~ A) 
    p_original[i] = summary(fit_original)$coefficients[2,4]
    if (p_original[i] < siglevel) {
      error_original[i] = 1 
    }
    transformed = INT_function(original, n, k) 
    fit_transformed = lm(formula = transformed ~ A)
    p_transformed[i] = summary(fit_transformed)$coefficients[2,4]
    if (p_transformed[i] < siglevel) {
       error_transformed[i] = 1
    }
  }
  print(data.frame("TypeI Error Rate Original" = (length(which(error_original == 1)))/simulation, "TypeI Error Rate Transformed" = (length(which(error_transformed == 1)))/simulation))
  hist(p_original, main = "Distribution of p-values for Original Data")
  hist(p_transformed, main = "Distribution of p-values for Transformed Data")
}
lognormfunc(1000, 20, 0.4, 0.05)
```
```{r}
lognormfunc(1000, 50, 0.4, 0.05)
```
```{r}
lognormfunc(1000, 100, 0.4, 0.05)
```

### Set sdlog = 2. Try different sample sizes
```{r}
lognormfunc = function(simulation, n, k, siglevel) {
  X1 = c(rep(1, n/2), rep(0, n/2))
  X2 = c(rep(0, n/2), rep(1, n/2))
  A = matrix(c(X1, X2), nrow = n, ncol=2)
  p_original = vector(length = simulation)
  error_original = NA
  p_transformed = vector(length = simulation)
  error_transformed = NA
  
  plot(density(rlnorm(n, meanlog = 0, sdlog = 2)), main = "Density Curve")
  for(i in 1 : simulation){
    original = rlnorm(n, meanlog = 0, sdlog = 2)
    fit_original = lm(formula = original ~ A) 
    p_original[i] = summary(fit_original)$coefficients[2,4]
    if (p_original[i] < siglevel) {
      error_original[i] = 1 
    }
    transformed = INT_function(original, n, k) 
    fit_transformed = lm(formula = transformed ~ A)
    p_transformed[i] = summary(fit_transformed)$coefficients[2,4]
    if (p_transformed[i] < siglevel) {
       error_transformed[i] = 1
    }
  }
  print(data.frame("TypeI Error Rate Original" = (length(which(error_original == 1)))/simulation, "TypeI Error Rate Transformed" = (length(which(error_transformed == 1)))/simulation))
  hist(p_original, main = "Distribution of p-values for Original Data")
  hist(p_transformed, main = "Distribution of p-values for Transformed Data")
}
lognormfunc(1000, 20, 0.4, 0.05)
```
```{r}
lognormfunc(1000, 50, 0.4, 0.05)
```
```{r}
lognormfunc(1000, 100, 0.4, 0.05)
```

### Set sdlog = 3. Try different sample sizes
```{r}
lognormfunc = function(simulation, n, k, siglevel) {
  X1 = c(rep(1, n/2), rep(0, n/2))
  X2 = c(rep(0, n/2), rep(1, n/2))
  A = matrix(c(X1, X2), nrow = n, ncol=2)
  p_original = vector(length = simulation)
  error_original = NA
  p_transformed = vector(length = simulation)
  error_transformed = NA
  
  plot(density(rlnorm(n, meanlog = 0, sdlog = 3)), main = "Density Curve")
  for(i in 1 : simulation){
    original = rlnorm(n, meanlog = 0, sdlog = 3)
    fit_original = lm(formula = original ~ A) 
    p_original[i] = summary(fit_original)$coefficients[2,4]
    if (p_original[i] < siglevel) {
      error_original[i] = 1 
    }
    transformed = INT_function(original, n, k) 
    fit_transformed = lm(formula = transformed ~ A)
    p_transformed[i] = summary(fit_transformed)$coefficients[2,4]
    if (p_transformed[i] < siglevel) {
       error_transformed[i] = 1
    }
  }
  print(data.frame("TypeI Error Rate Original" = (length(which(error_original == 1)))/simulation, "TypeI Error Rate Transformed" = (length(which(error_transformed == 1)))/simulation))
  hist(p_original, main = "Distribution of p-values for Original Data")
  hist(p_transformed, main = "Distribution of p-values for Transformed Data")
}
lognormfunc(1000, 20, 0.4, 0.05)
```
```{r}
lognormfunc(1000, 50, 0.4, 0.05)
```
```{r}
lognormfunc(1000, 100, 0.4, 0.05)
```
